% Za FFT ako budes pisao
% https://www.ncbi.nlm.nih.gov/pmc/articles/PMC330830/pdf/nar00194-0150.pdf

\begin{thebibliography}{}

% https://doi.org/10.1137/0206024
\bibitem{kmprad} Knuth D.E, Morris J.H, Pratt V.R. \textit{Fast Pattern Matching in Strings}. SIAM Journal on Computing, 1977, Vol. 6, No. 2 : pp. 323-350

% https://doi.org/10.1017/CBO9780511574931
\bibitem{zalgoknjiga} Gusfield D. \textit{Algorithms on Strings, Trees, and Sequences}. Cambridge University Press, 1997

% https://doi.org/10.1145/360825.360861
\bibitem{hirschbergrad} Hirschberg D.S. \textit{A linear space algorithm for computing maximal common subsequences}. Comm. A.C.M. 18(6) p341-343, 1975

% https://doi.org/10.1162/089120100750105975
\bibitem{levenshteinknjiga} Jurafsky D, Martin J.H. \textit{Speech and Language Processing}. Pearson Education International, 2000

% https://doi.org/10.1145/360825.360855
\bibitem{ahorad} Aho A.V, Corasick M.J. \textit{Efficient string matching: an aid to bibliographic search}. Comm. A.C.M. 18(6) p333-340, 1975

% https://doi.org/10.1007/10719839_9
\bibitem{lcarmqrad} Bender M.A., Farach-Colton M. \textit{The LCA Problem Revisited}. Gonnet G.H., Viola A. (eds) LATIN 2000: Theoretical Informatics. LATIN 2000. Lecture Notes in Computer Science, vol 1776. Springer, Berlin, Heidelberg

% https://doi.org/10.1137/0222058
\bibitem{sufiksnizprvirad} Manber U, Myers G. \textit{Suffix arrays: a new method for on-line string searches}. SIAM J Comput. 1993;22(5):935--48.

% https://doi.org/10.1007/3-540-48194-X_17
\bibitem{lcpnizrad} Kasai T, Lee G, Arimura H, Arikawa S, Park K. \textit{Linear-Time Longest-Common-Prefix Computation in Suffix Arrays and Its Applications}. Amir A. (eds) Combinatorial Pattern Matching. CPM 2001. Lecture Notes in Computer Science, vol 2089. Springer, Berlin, Heidelberg

% https://doi.org/10.1007/BF01206331
\bibitem{suffixtreerad} Ukkonen E. \textit{On-line construction of suffix trees}. Algorithmica (1995) 14: 249. 

% \bibitem{thuemorserad} Allouche JP., Shallit J. \textit{The Ubiquitous Prouhet-Thue-Morse Sequence}. Ding C., Helleseth T., Niederreiter H. (eds) Sequences and their Applications. Discrete Mathematics and Theoretical Computer Science. Springer, London

\bibitem{sortnlogn} https://en.cppreference.com/w/cpp/algorithm/sort

\end{thebibliography}

